Scheeper's Meager-NWD Game and the Menger Game

### 2014-11-24 phd/dissertation/chapter3.tex
fix issues found in seminar

Since it's trivial to show that $\pl O\prewin\gruConGame{\oneptcomp\kappa}$ if and
only if $\kappa\leq\omega$, this closes the question on limited information
strategies for $\gruConGame{\oneptcomp\kappa}{\infty}$. However, limited
information analysis of the harder $\gruConGameHard{\oneptcomp\kappa}{\infty}$
is more interesting.

>>>>

Since it's trivial to show that
$\pl O\prewin\gruConGame{\oneptcomp\kappa}{\infty}$ if and
only if $\kappa\leq\omega$, this closes the question on limited information
strategies for $\gruConGame{\oneptcomp\kappa}{\infty}$. However, limited
information analysis of the harder $\gruConGameHard{\oneptcomp\kappa}{\infty}$
is more interesting.
